---
title: "What the Newspapers industries decline after TV advertising"
author: 'Chang Xu,1003791550'
date: '2020-12-18'
output:
  pdf_document: default
  html_document:
    df_print: paged
abstract: 'This article studies the impact of TV advertising on the newspaper industry from the advertising side and reader side. By analyzing the French data from 1960 to 1974, the difference in difference method results shows that, as a substitute, TV advertising will negatively impact the newspaper industry. The impact includes a decrease in revenue and a decrease in circulation, but an absolute increase in the subscription and individual purchase prices. '
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(haven)
#library(dplyr)
#library(ggplot2)
library(huxtable)
#library(scales)


```

**keywords**: Difference in Difference, Newspapers, Advertising Revenues

## Introduction

Nowadays, the popularity of newspaper advertising is far lower than that of TV and the Internet. The decline of the newspaper industry is inevitable, but when did the newspaper industry decline and from which aspects are the main research content of this article.

As the earliest media, the newspaper industry accounted for most of the advertising industry before 1960. However, with the permission of television advertising, the newspaper industry began to decline. The newspaper industry can be divided into national newspapers and local newspapers. Angelucci's article pointed out that TV advertising's popularity has a more significant impact on national newspapers than local newspapers. Angelucci analyzed the French data from 1960 to 1974, studied the influence of TV advertising on newspaper publishers and readers, and used the Difference in Difference method to fit the data with high research value. This article will then reproduce and analyze the main research results in the report.

The article is mainly divided into the following parts. First, the source and description of the data is given, then introduces the principle of the difference in difference method, and gives the response of publishers and readers to the impact of TV advertisements, and finally discusses and analyzes TV advertisements through the estimated model Brings a series of changes in the newspaper industry.


## Data

The data set contains annual data on French local and national newspapers between 1960 and 1974,  and detailed information about TV content. Data includes the advertising side and reader side output. Advertising side data mainly includes revenue, number of journalists, circulation, newspaper pages, and share of advertising, while reader side data includes newspaper price, the share of subscription, etc.

In 1967, the French government announced that it would relax the long-term ban on television advertising. This regulation has different effects on local newspapers and national newspapers, so we describe these variables separately. There are 1196 observations, 180 obs for national paper, 1015 obs for local paper. Table 1 shows the national newspaper industry data, and Table 2 shows the local newspaper data. Through comparison, we can find that there are more local newspapers than national newspapers. The revenue and circulation of national newspapers are higher than those of local newspapers.

To reflect the impact of TV advertising on the national and the local newspaper industry, the trend changes for publishers' side data are shown in Figure 1. The change of data from the reader's side is shown in Figure 2. 



```{r,echo = FALSE}

newspapers <- read_dta("Angelucci_Cage_AEJMicro_dataset.dta")
newspapers <- newspapers %>% 
  dplyr::select(year,  after_national, local, national, # Diff in diff variables
        id_news, ra_cst, rtotal_cst,ps_cst, po_cst, rs_cst, ra_s,nb_journ,qtotal, ads_p4_cst, ads_s,id_news, # Advertising side dependents
         qtotal, qs_s,pages,news_hole, ads_q) %>% 
  mutate(ra_cst_div_qtotal = ra_cst / qtotal) %>% # An advertising side dependents needs to be built
  mutate_at(vars(id_news, after_national, local, national), ~as.factor(.)) %>% # Change some to factors
  mutate(year = as.integer(year))

nationalnewspaper <- subset(newspapers,newspapers$national == 1)
localnewspaper <- subset(newspapers,newspapers$national == 0)
#length(nationalnewspaper$rtotal_cst)
#summary(nationalnewspaper)
#summary(localnewspaper)

```

\newpage


**Table 1 --Summary statistics: National Daily Newspapers**

|                  |  Mean| Median| SD|  Min| Max| Observations|
|:-----------------|----:|---:|----:|---:|----:|---:|
| **Price**    |
|Unit buy price         | 3.6|   3.5|  1.3| 2.4|9.3| 152|
|Subscription price per issue     | 2.8|   2.7|  0.7| 1.9|5.6| 148|
|Display ad rate(listed price)       |121.1| 114.5| 81.0| 17.5|274.2| 121|
| **Revenues and journalists**    |
|Total Revenues        | 425|   271| 403 | 19|1482| 162|
|Revenues from advertising     |228| 103| 258| 7|864| 161|
|Revenues from sales       | 199|  145| 181| 12|657| 162|
|Share of advertising in total revenues       | 47.4|   51.1|  21.3|  8.0|81.0|  162|
|Number of journalists       | 117|   85|  81|  21|326|  158|
| **Circulation**    |
|Total circulation        | 295210|   181574|  292838| 16112|1143676| 162|
|Share of subscribers    | 25.6|   18.5|  26.3| 0.7|92.3| 163|
| **content**    |
|Number of pages       | 19|   17|  7|  8|38|  138|
|Newshole (nonadvertising space)       | 13|   13|  4|  6|25|  138|
|Advertising space       | 5|   4|  4|  0|16|  138|






**Table 2 --Summary statistics: Local Daily Newspapers**

|                  |  Mean| Median| SD|  Min| Max| Observations|
|:-----------------|----:|---:|----:|---:|----:|---:|
| **Price**    |
|Unit buy price         | 3.2|   3.3|  0.8| 0.8|5.7| 911|
|Subscription price per issue     | 2.8|   2.7|  0.7| 0.7|4.7| 896|
|Display ad rate(listed price)       |80.3| 57.7| 72.6| 3.8|327.2| 688|
| **Revenues and journalists**    |
|Total Revenues        | 146|   65| 176 | 1|1026| 888|
|Revenues from advertising     |67| 30| 79| 1|416| 891|
|Revenues from sales       | 79|  36| 102| 0|751| 884|
|Share of advertising in total revenues       | 46.5|   45.9|  8.3|  7.1|70.4|  878|
|Number of journalists       | 53|   27|  58|  1|297|  907|
| **Circulation**    |
|Total circulation        | 101487|   50586|  119774| 1480|654992| 908|
|Share of subscribers    | 27.5|   23.3|  22| 1.0|100.1| 909|
| **content**    |
|Number of pages       | 15|   15|  6|  2|66|  908|
|Newshole (nonadvertising space)       | 12|   12|  4|  2|34|  908|
|Advertising space       | 3|   2|  3|  0|32|  908|



```{r,echo = FALSE}
local_res <- localnewspaper %>%
  group_by(year) %>%
  summarise(revenue = mean(log(ps_cst),na.rm = TRUE), 
            revenue_ciculation = mean(log(ra_cst_div_qtotal),na.rm = TRUE),  
            ad_price = mean(log(ads_p4_cst),na.rm = TRUE), 
            ad_space = mean(log(ads_s),na.rm = TRUE),.groups = 'drop')
ts_local_res <- ts(local_res, start = 1960)

national_res <- nationalnewspaper %>%
  group_by(year) %>%
  summarise(revenue = mean(log(ra_cst),na.rm = TRUE), 
            revenue_ciculation = mean(log(ra_cst_div_qtotal),na.rm = TRUE),  
            ad_price = mean(log(ads_p4_cst),na.rm = TRUE), 
            ad_space = mean(log(ads_s),na.rm = TRUE),.groups = 'drop')

ts_national_res <- ts(national_res, start = 1960)
```



```{r,echo = FALSE, fig.cap = "Trend of local and national advertising"}
par(mfrow = c(2,2))

ts.plot(ts_national_res[,2],ts_local_res[,2],col = c(1,2),main = "comparison of Ad revenue")
abline(v = 1967)

ts.plot(ts_national_res[,3],ts_local_res[,3],col = c(1,2),main = "comparison of revenues from ciculation")
abline(v = 1967)

ts.plot(ts_national_res[,4],ts_local_res[,4],col = c(1,2),main = "comparison of Ad price")
abline(v = 1967)

ts.plot(ts_national_res[,5],ts_local_res[,5],col = c(1,2),main = "comparison of Ad space")
abline(v = 1967)


```




```{r,echo = FALSE, fig.cap = "Trend of local and national advertising"}
L_reader_res <- localnewspaper %>%
  group_by(year) %>%
  summarise(Subscription_price = mean(log(ra_cst),na.rm = TRUE), 
            Unit_price = mean(log(ra_cst_div_qtotal),na.rm = TRUE),  
            Ciculation = mean(log(qtotal),na.rm = TRUE), 
            Share_of_substribers = mean(log(qs_s),na.rm = TRUE),
            Revenue_from_sale = mean(log(rs_cst),na.rm = TRUE),.groups = 'drop')
ts_L_reader_res <- ts(L_reader_res, start = 1960)

N_reader_res <- nationalnewspaper %>%
  group_by(year) %>%
  summarise(Subscription_price = mean(log(ra_cst),na.rm = TRUE), 
            Unit_price = mean(log(ra_cst_div_qtotal),na.rm = TRUE),  
            Ciculation = mean(log(qtotal),na.rm = TRUE), 
            Share_of_substribers = mean(log(qs_s),na.rm = TRUE),
            Revenue_from_sale = mean(log(rs_cst),na.rm = TRUE),.groups = 'drop')
ts_N_reader_res <- ts(N_reader_res, start = 1960)


par(mfrow = c(3,2))

ts.plot(ts_N_reader_res[,2],ts_L_reader_res[,2],col = c(1,2),main = "comparison of subscription price")
abline(v = 1967)

ts.plot(ts_N_reader_res[,3],ts_L_reader_res[,3],col = c(1,2),main = "comparison of unit price")
abline(v = 1967)

ts.plot(ts_N_reader_res[,4],ts_L_reader_res[,4],col = c(1,2),main = "comparison of circulation")
abline(v = 1967)

ts.plot(ts_N_reader_res[,5],ts_L_reader_res[,5],col = c(1,2),main = "comparison of share of subscribers")
abline(v = 1967)

ts.plot(ts_N_reader_res[,6],ts_L_reader_res[,6],col = c(1,2),main = "comparison of Revenue from sale")
abline(v = 1967)
```



## Model

The difference in difference regression equation is :

$$y_{n,t} = \alpha + \beta_t (D_{after} * D_{nationalnews})+\lambda_n+\gamma_t+ e_{n,t}$$

where $y_{n,t}$ is the outcome of interest
$D_{after}$ is the time dummy to indicator before and after 1967
$D_{nationalnews}$ is an indicator variable for national newspaper
$\lambda_n$ is the fixed effect for newspaper
$\gamma_t$ is the fixed effect for time. 

The outcome of interest includes these variables on the advertising side of the market and variables on the price of the reader side. The outcome of interest are all in the logrithms form. In order to use difference in difference to analyze, the data need to meet the parallel line assumption. 

## Results 

The results of Model 1 show that TV advertising has a substitute effect on the newspaper industry. For example, the revenue and advertising prices of newspapers will have a significant drop. However, the impact of advertising space in newspapers is minimal. On the other hand, we have added the fixed effect of year, and the estimated beta value eliminates the influence of time on TV commercial effects. We can see that although the impact of television on the newspaper industry is negative, the newspaper industry still has an upward trend over time. This can also be reflected in Figure 1 above.

Secondly, the results of Model 2 show that after the emergence of TV advertisements, newspapers' subscription price has a certain downward trend, and the circulation of newspapers has also declined significantly. The income from newspaper sales has also declined. However, with the advent of TV ads, the unit price of individual sale has increased, and the proportion of people who subscribe were also increased.



```{r,echo = FALSE}
# Advertising side
ad_revenue <- lm(log(ra_cst) ~ after_national +  id_news + year, data = newspapers)
ad_revenue_div_circulation <- lm(log(ra_cst_div_qtotal) ~ after_national + id_news + year, data = newspapers)
ad_price <- lm(log(ads_p4_cst) ~ after_national + id_news + year, data = newspapers)
ad_space <- lm(log(ads_s) ~ after_national + id_news + year, data = newspapers)

# Consumer side
subscription_price <- lm(log(ps_cst) ~ after_national + id_news + year, data = newspapers)
unit_price <- lm(log(po_cst) ~ after_national + id_news + year, data = newspapers)
circulation <- lm(log(qtotal) ~ after_national + id_news + year, data = newspapers)
share_of_sub <- lm(log(qs_s) ~ after_national + id_news + year, data = newspapers)
revenue_from_sales <- lm(log(rs_cst) ~ after_national + id_news + year, data = newspapers)

```

**Table 3 Advertising side**

```{r,echo = FALSE}
omit_me <- c("(Intercept)", "id_news3", "id_news6", "id_news7", "id_news13", 
             "id_news16", "id_news25", "id_news28", "id_news34", "id_news38", 
             "id_news44", "id_news48", "id_news51", "id_news53", "id_news54", 
             "id_news57", "id_news60", "id_news62", "id_news66", "id_news67", 
             "id_news70", "id_news71", "id_news72", "id_news80", "id_news82", 
             "id_news88", "id_news95", "id_news97", "id_news98", "id_news103", 
             "id_news105", "id_news106", "id_news118", "id_news119", "id_news127", 
             "id_news136", "id_news138", "id_news148", "id_news151", "id_news153", 
             "id_news154", "id_news157", "id_news158", "id_news161", "id_news163", 
             "id_news167", "id_news169", "id_news179", "id_news184", "id_news185", 
             "id_news187", "id_news196", "id_news206", "id_news210", "id_news212", 
             "id_news213", "id_news224", "id_news225", "id_news234", "id_news236", 
             "id_news245", "id_news247", "id_news310", "id_news452", "id_news467", 
             "id_news469", "id_news480", "id_news20040", "id_news20345", 
             "id_news20346", "id_news20347", "id_news20352", "id_news20354", 
             "id_news21006", "id_news21025", "id_news21173", "id_news21176", 
             "id_news33718", "id_news34689", "id_news73")


huxreg("Ad. rev." = ad_revenue, 
       "Ad rev. div. circ." = ad_revenue_div_circulation, 
       "Ad price" = ad_price, 
       "Ad space" = ad_space,
       omit_coefs = omit_me, 
       number_format = 2
)


```


## Discussion

This article studies the impact of TV advertisements in the newspaper industry, from both the advertising side and reader side to analyze the effects. The results show that, as a new form of advertising, TV advertising presents a substitution effect. This shock caused the revenue and circulation of the newspaper industry to be negative. However, this does not represent a decline in the overall data of the newspaper industry. From the previous trend chart, we can still find that the overall newspaper industry still has an upward trend over time. By adding the fixed effect to the model, we can effectively eliminate the time factor's influence, thereby obtaining a more accurate estimate of the treatment effect.

\newpage

**Table 4 Reader side**
```{r,echo = FALSE}
omit_me <- c("(Intercept)", "id_news3", "id_news6", "id_news7", "id_news13", 
             "id_news16", "id_news25", "id_news28", "id_news34", "id_news38", 
             "id_news44", "id_news48", "id_news51", "id_news53", "id_news54", 
             "id_news57", "id_news60", "id_news62", "id_news66", "id_news67", 
             "id_news70", "id_news71", "id_news72", "id_news80", "id_news82", 
             "id_news88", "id_news95", "id_news97", "id_news98", "id_news103", 
             "id_news105", "id_news106", "id_news118", "id_news119", "id_news127", 
             "id_news136", "id_news138", "id_news148", "id_news151", "id_news153", 
             "id_news154", "id_news157", "id_news158", "id_news161", "id_news163", 
             "id_news167", "id_news169", "id_news179", "id_news184", "id_news185", 
             "id_news187", "id_news196", "id_news206", "id_news210", "id_news212", 
             "id_news213", "id_news224", "id_news225", "id_news234", "id_news236", 
             "id_news245", "id_news247", "id_news310", "id_news452", "id_news467", 
             "id_news469", "id_news480", "id_news20040", "id_news20345", 
             "id_news20346", "id_news20347", "id_news20352", "id_news20354", 
             "id_news21006", "id_news21025", "id_news21173", "id_news21176", 
             "id_news33718", "id_news34689", "id_news73")

huxreg("Subscription price" = subscription_price, 
       "Unit price" = unit_price, 
       "Circulation" = circulation, 
       "Share of sub" = share_of_sub,
       "Revenue from sales" = revenue_from_sales,
       omit_coefs = omit_me, 
       number_format = 2
)
```




## Weaknesses

However, a serious problem in Charles Angelucci's paper is that the assumption of difference in difference regression method may not hold. His paper only check the price ratio satisfied the assumption. Through the analysis in the data section, it can be seen that the log data after entering the transformation do not meet the assumptions well. Therefore, the conclusion of Difference in Difference is not very reliable.

## References

Charles Angelucci, Julia Cage. Newspapers in Times of Low Advertising Revenues. 2015.
Difference in differences. (2020, November 05). Retrieved December 20, 2020, from 

Rohan, A. (2020, November 05). Difference in differences. Retrieved December 20, 2020, from https://www.tellingstorieswithdata.com/06-03-matching_and_differences.html


